Modelling BCG vaccination in the UK

### 2019-12-03 rmds/03-getTBinR.Rmd
updated getTBinR title
added getTBinR corrections

# getTBinR: an R package for accessing and summarising the World Health Organization Tuberculosis data {#getTBinR}

@@

Whilst `getTBinR` is feature complete, and stable, development work continues. Future projects include: using the `shinymeta` R package to provide downloadable R code to users of the interactive application; iterating on the current automated report to improve formatting and to increase the amount of information displayed, and expanding the range of visualisation functions available. As additional WHO TB data are released they will be added to `getTBinR`.

>>>>

# getTBinR: an R package for accessing and summarising World Health Organization Tuberculosis data {#getTBinR}

@@

Whilst `getTBinR` is feature complete, and stable, development work continues. Future projects include: using the `shinymeta` R package to provide downloadable R code to users of the interactive application; iterating on the current automated report to improve formatting and to increase the amount of information displayed; and expanding the range of visualisation functions available. As additional WHO TB data are released they will be added to `getTBinR`.
